Type Safe Redis Queries:\\A Case Study of Type-Level Programming in Haskell

### 2017-08-19 TyDe2017/main-tyde.tex
New acmart.cls and acmthm.sty, to fix font problem.
Minor changes regarding font issues.
No-copyright footnote.

\documentclass[sigplan, screen, 9pt]{acmart}
\settopmatter{printfolios=true}

@@

\title{Type Safe Redis Queries: A Case Study of Type-Level Programming in Haskell}

>>>>

\documentclass[sigplan]{acmart}
\settopmatter{printfolios=true}

@@

\title{Type Safe Redis Queries:\\A Case Study of Type-Level Programming in Haskell}

\titlenote{\copyright\ \!\!\!\!\!\!\!\! $\slash$ ~~~ No Copyright. This work is in the public domain. For avoidance of
doubt, this work is released under the CC0 Public Domain Dedication
(\url{http://creativecommons.org/publicdomain/zero/1.0/}). Please search
for free copy.}
